Polyglots: Crossing Origins by Crossing Formats

### 2013-08-11 main.tex
Progress on the TODO list

@@

\paragraph{Content smuggling}
Further, a smaller study was conducted, not covering the full Alexa top 100, but 
targeting popular cloud storage services. 
This study is based on polyglot content being uploaded to the service and 
subsequently analyzed to determine which origin it was served 
under. We have found two major 
enterprise cloud storage services to be susceptible to attacks. Both services make an effort to
follow current best practices, see Section~\ref{sec:smuggling-mitigation}, but 
fail to cover scenarios for content upload.

@@

%1-2 pages 
\section{Mitigation}
\label{sec:mit}
This section gives advice on various mitigation approaches available for each of the
affected components, both server-side and client-side. It should be noted that 
preventing polyglot attacks in the general case is a complex task, as one would 
need to take all potentially malicious formats in to account. Mitigating instances of 
polyglot attacks based on particular formats are significantly more straightforward.

Note that although some mitigation discussed below is already in place
(notably as implemented by the Chrome builtin PDF reader), the state of the art
is far from being satisfactory. As our paper demonstrates, the
polyglot attacks are a real threat. It is the paper's main value to
bring attention to polyglot attacks and the importance of
mitigation against them.

\subsection{Server-side mitigation}

@@

\subsubsection{Syntax injection}

@@

\subsubsection{Content smuggling}
\label{sec:smuggling-mitigation}
The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
on hosting user-supplied content, is to serve the content from a sandboxed origin that is 
completely separate, as per SOP, and isolated from the sensitive services. 
These best-practices successfully prevents content smuggling 
attacks, as the restrictions of the SOP prevents the content from accessing any sensitive 
resources in the origin of the web service.

@@

\subsection{Browser}

@@

In the case of PDF-based polyglots, the browser can intervene when there is a 
mismatch between the content-type provided by the server and the type attribute 
of the \emph{object} tag. The vulnerability can be mitigated by acknowledging that there is a potential security issue in 
interpreting the supplied content in the requested format and alerting the user to this
threat.

@@

\subsection{Interpreter}

@@

\appendix

\section{Code samples}
\begin{lstlisting}[label=lst:sample-pdf, caption=Sample PDF file]
%PDF-1.4
1 0 obj
<< /Type /Catalog
   /Outlines 2 0 R
   /Pages 3 0 R
>>
endobj
2 0 obj
<< /Type Outlines
   /Count 0
>>
endobj
3 0 obj
<< /Type /Pages
   /Kids [4 0 R]
   /Count 1
>>
endobj
4 0 obj
<< /Type /Page
   /Parent 3 0 R
   /MediaBox [0 0 612 792]
   /Contents 5 0 R
   /Resources << /ProcSet 6 0 R >>
>>
endobj
5 0 obj
<< /Length 35 >>
stream
   ...Page-marking operators...
endstream
endobj
6 0 obj
   [/PDF]
endobj
xref
0 7
0000000000 65535 f
0000000009 00000 n
0000000074 00000 n
0000000120 00000 n
0000000179 00000 n
0000000300 00000 n
0000000384 00000 n
trailer
<< /Size 7
   /Root 1 0 R
>>
startxref
408
%%EOF
\end{lstlisting}

>>>>

\begin{lstlisting}[label=lst:sample-pdf, caption=Sample PDF file]
%PDF-1.4
1 0 obj
<< /Type /Catalog
   /Outlines 2 0 R
   /Pages 3 0 R
>>
endobj
2 0 obj
<< /Type Outlines
   /Count 0
>>
endobj
3 0 obj
<< /Type /Pages
   /Kids [4 0 R]
   /Count 1
>>
endobj
4 0 obj
<< /Type /Page
   /Parent 3 0 R
   /MediaBox [0 0 612 792]
   /Contents 5 0 R
   /Resources << /ProcSet 6 0 R >>
>>
endobj
5 0 obj
<< /Length 35 >>
stream
   ...Page-marking operators...
endstream
endobj
6 0 obj
   [/PDF]
endobj
xref
0 7
0000000000 65535 f
0000000009 00000 n
0000000074 00000 n
0000000120 00000 n
0000000179 00000 n
0000000300 00000 n
0000000384 00000 n
trailer
<< /Size 7
   /Root 1 0 R
>>
startxref
408
%%EOF
\end{lstlisting}

@@

\paragraph{Content smuggling}
Further, a smaller study was conducted, not covering the full Alexa top 100, but 
targeting popular cloud storage services. 
This study is based on polyglot content being uploaded to the service and 
subsequently analyzed to determine which origin it was served 
under. We have found two major 
enterprise cloud storage services to be susceptible to attacks. Both services make an effort to
follow current best practices, see Section~\ref{sec:smuggling-mitigation}, but 
fail to cover certain scenarios for content upload.

@@

%1-2 pages 
\section{Mitigation}
\label{sec:mit}
This section gives advice on various mitigation approaches available for each of the
affected components, both server-side and client-side. 
We provide one general mitigation approach that covers a significant segment of 
the potential attack vectors, and provide specific mitigation suggestions for affected 
components.

Note that although some of the mitigation suggestions discussed below are already in place
(notably as implemented by the Chrome builtin PDF reader), the state of the art
is far from being satisfactory. As our paper demonstrates, the
polyglot attacks are a real threat. It is the paper's main value to
bring attention to polyglot attacks and the importance of
mitigation against them.

\subsection{General approach}
It should be noted that 
preventing polyglots, and thereby polyglot attacks, in the general case is a complex task, as one would 
need to take all potentially malicious formats in to account. Mitigating instances of 
polyglot attacks based on particular formats are significantly more straightforward. 
Our approach is not attempting to prevent polyglots as such, but provide details about 
the context in which the content will be interpreted, such that an informed decision 
can be made on whether rendering the content constitutes a security risk or not.

The relation between web server and the browser is central in a web environment, but 
there is no common agreement on the type of content communicated between server 
and client. As mentioned in Section~\ref{sec:cross-origin}, in each response the web server sends a 
header representing its view on the type of content delivered, however, the browser
is free to ignore the provided type and can even be instructed to do so.
Often the browser knows precisely the context in which the content will be 
rendered and the types suitable for these contexts. 
%
As an example, when content is loaded in an object-tag with a type attribute, as 
is the case throughout the paper, the browser already
has exact knowledge as to which types the requested content can be interpreted as in this context. A natural
defense technique is to send the expected types along with the request. The web server
then compares the expected types to the assumed type and react accordingly, e.g., 
if the assumed type is HTML and the expected type is PDF, an 
error can be sent back to the client. On the client side, the browser verifies 
the type in the response matches any of the expected types, possibly alerting 
the user if there is a mismatch. This mutual agreement between client and server
can help mitigate both syntax injection and content smuggling.
Furthermore, this approach can be implemented in the
web server itself, as opposed to a web application, since the web server makes the
final decision on the supplied content-type.

The expected type is useful also to a web application that performs content 
filtering on the fly. At the point when the content is being requested, it only 
requires verification against the expected type.

There are limitations to this technique; If a context has multiple possible types, e.g., an image-tag, 
a polyglot between two of the types can evade detection. The specific cases where this situation 
occurs in an exploitable way are rare, and further work can help in determining and mitigating such 
vulnerabilities.

\subsection{Specific approaches}

Apart from the general approach described above, there are mitigation approaches 
that are specific to each of the components involved. These are recommended to 
be used until general approaches for mitigating polyglot attacks are widely adopted.

\subsubsection{Server-side mitigation}

@@

\paragraph{Syntax injection}

@@

\paragraph{Content smuggling}
\label{sec:smuggling-mitigation}
The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
on hosting user-supplied content, is to serve the content from a sandboxed origin that is 
completely separate, as per SOP, and isolated from the sensitive services. 
These best-practices successfully prevents content smuggling 
attacks, as the restrictions of the SOP prevents the content from accessing any sensitive 
resources in the origin of the web service.

@@

\subsubsection{Browser}

@@

In the case of PDF-based polyglots, and other polyglots that require a plugin, the browser can intervene when there is a 
mismatch between the content-type provided by the server and the type attribute 
of the \emph{object} tag. The vulnerability can be mitigated by acknowledging that there is a potential security issue in 
interpreting the supplied content in the requested format and alerting the user to this
threat.

@@

\subsubsection{Interpreter / Plugin}

@@
